### 2003-12-02 Documentation/part1.tex
*** empty log message ***

@@

\bi
\item
 More technical: what does it do; how to imagine; what functions are there; examples
 Single/multiple experiments and the connection (sum of individual $\chi$'s )
\item
 Advanced topic: Changing the systematics treatment (SetErrorDim)
\ei

>>>>

To be written later: Short introduction such as ``With the following lines we obtain ...''
without detailed description of parameters. Should contain all most important functions of \GLOBES\ --
overview of main functions in \tabl{stdfunctions}.
Maybe: in form of long example which involves everything (for example: our famous bar plot, which involves
systematics, correlations, degeneracies and thus the full set of \GLOBES\ functions without being too
complicated in the application software part).

@@

\bi
\item
 More technical: what does it do (minimizer); how to imagine (simple example); 
what functions are there; examples
\item
 Single/multiple experiments and the connection (sum of individual $\chi$'s )
\item
 Advanced topic: Changing the systematics treatment (SetSystematics)
\ei
